Lobbying and Legislative Uncertainty

### 2016-05-09 presentation.tex
proof read for presentation at Midwest
more adjustments for Midwest talk
minor improvements to overview and model sec of presentation

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{April 16, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\pause
\begin{enumerate}[<+->]
\item How does uncertainty about legislators' preferences impact 
	\begin{itemize}
		\item lobbying strategies (e.g. who to lobby, how much to `pay')
		\item probability a bill passes
	\end{itemize}
	\vskip.1in
\item Can we distentangle fundamental uncertainty about preferences from equilibrium and modeling uncertainty?
	\begin{itemize}
		\item[$\Rightarrow$] Build a structural model to take to U.S. House data
	\end{itemize}
	\vskip.1in
\item Ultimately, want to identify cross-industry measures of legislative uncertainty
\end{enumerate}

@@

@@

\begin{frame}{Literature}
\pause
\begin{itemize}[<+->]
	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets (2007)
	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
	%\item \textbf{Uncertainty}: 
\end{itemize}
\end{frame}

@@

\vskip.2in
\pause
Use multi-dimensional ideal-point estimation to identify measures of uncertainty
\end{frame}

@@

\pause
Three legislators
\pause
\begin{itemize}
	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
	\item Decision made by majority vote
\end{itemize}

\pause
\vskip.2in
Two vote buyers, $A$ and $B$
\pause
\begin{itemize}
	\item A prefers $x$, $B$ prefers $s$
\end{itemize}

@@

\begin{frame}{Legislators}
\pause
Take ideal point to be linear: $\alpha - \beta i$
\pause
\begin{itemize}[<+->]
	\item Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
		\begin{itemize}
			\item Probability $i$ votes for $s$ is $\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right] = \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right] $
			\item Assuming $\ta \sim \text{Logistic} \ (0,1)$, it's $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
		\end{itemize}
\end{itemize}

@@

\begin{frame}{Vote Buyer B}
\pause
Assume vote buyers maximize expected value of winning net of bribes paid  
\begin{itemize}[<+->]
	\item Assume bribes must be non-negative
	\item Vote buyer won't spend more than his willingness to pay, $W_B$
	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s$
\end{itemize}
\end{frame}

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $X(i) = 1$ denote legislator $i$ votes for the status quo
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\begin{itemize}[<+->]
	\item She gets to move first
	\item She wants $x$ to win instead of $s$
\end{itemize}
\end{frame}

>>>>

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\pause
\begin{enumerate}[<+->]
\item How does uncertainty about legislators' preferences impact 
	\begin{itemize}
		\item lobbying strategies (e.g. who to lobby, how much to `pay')
		\item probability a bill passes
	\end{itemize}
	\vskip.1in
\item Can we distentangle fundamental uncertainty about preferences from equilibrium and modeling uncertainty?
	\begin{itemize}
		\item[$\Rightarrow$] build a structural model to take to U.S. House data
	\end{itemize}
	\vskip.1in
\item Ultimately, want to identify cross-industry measures of legislative uncertainty
	\begin{itemize}
		\item but for today, unidimensional model
	\end{itemize}
\end{enumerate}

@@

\begin{frame}{Literature}
\pause
\begin{itemize}[<+->]
	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets 2007
	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
	\item \textbf{Influence w/out Vote Buying}: Fox $\&$ Rothenberg 2011
\end{itemize}
\end{frame}

@@

@@

\vskip.2in
\pause
Goal: use multi-dimensional ideal-point estimation to identify measures of uncertainty
\end{frame}

@@

\pause
Two vote buyers, $A$ and $B$
\pause
\begin{itemize}
	\item A prefers $x$, $B$ prefers $s$
\end{itemize}

\pause
\vskip.2in
Three legislators
\pause
\begin{itemize}[<+->]
	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
	\item Decision made by majority vote
	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,0.5\right\}$
		\begin{itemize}
			\item Take ideal point to be linear: $\alpha - \beta i$
		\end{itemize}
\end{itemize}

@@

\begin{frame}{Legislators}

\pause
Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
	\begin{itemize}[<+->]
		\item Probability $i$ votes for $s$ is
			\[ 
				\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right]
			\]
			\[
				= \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right]
			\]
		\item Assuming $\ta_i \text{ i.i.d.} \sim \text{Logistic} \ (0,1): \ = \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
	\end{itemize}

@@

\begin{frame}{Vote Buyer B}
\pause
Assume vote buyers maximize expected value of winning net of bribes paid  
\pause
\begin{itemize}[<+->]
	\item Assume bribes must be non-negative
	\item Vote buyer won't spend more than his willingness to pay, $W_B$
	\item In three-seat legislature, maximize $[$ probability $\geq 2$ legislators vote for $s ]$ $\times W_B -$ bribes
\end{itemize}
\end{frame}

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $X(i) = 1$ denote legislator $i$ votes for the status quo
\pause
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\pause
\begin{itemize}[<+->]
	\item She gets to move first
	\item She wants $x$ to win instead of $s$
	\item Willingness-to-pay parameter $W_A$
\end{itemize}
\end{frame}
